Generating the Blueprints of the Java Ecosystem

### 2015-02-27 msr.tex
abstract - draft

\maketitle
\begin{abstract}

\end{abstract}

>>>>

\maketitle
\begin{abstract}
Examining a large number of software artifacts can provide
the research community with data regarding quality an design.
We present a dataset obtained by statically analyzing
22730 {\sc jar} files taken from the Maven
central repository ecosystem. For our analysis
we used three popular static analysis tools
that calculate metrics regarding object-oriented design,
program size, and package design.
The dataset contains the metrics results that every tool
reports for every selected {\sc jar} of the
ecosystem. Our dataset can be used to produce interesting
research results, as we show in specific examples.
\end{abstract}
